Born in Seattle in 1955, Bill Gates has grown up in a very competitive family environment, a famous businesswoman as a mother and an important lawyer as a father, that rewarded and penalized every action remarkably hard. This stimulated Gates' propensity for competition and success throughout his whole life. \\
At the age of 13 he first came into contact with a Teletype Model 33 ASR terminal. This system triggered a spark in him that will never die; he started skipping classes to have time to work on that system, he wrote his first pieces of code that allowed the user to play Tic Tac Toe against the computer and he was hired by the Computer Center Corporation company as a bug-solver. \\
After a few attempts, more instructive than profitable, Gates created Microsoft together with his friend and future partner Paul Allen. The innovation that enabled Microsoft to gain popularity was that it literally put the computer into the everyday life of every single person.  It created the operating system for personal computers, starting from MS-DOS for early IBM machines and then the first release of Windows in 1985s. He provided the software for everyone’s computers: "A computer on every desktop and in every home" was his motto. Windows has completely revolutionized the way we think and use a computer, it has laid the foundations for the development of computer technology that we have today. Although GUIs (Graphical User Interfaces) had been invented and implemented firstly in the Macintosh computer, with Windows 1 in 1985 he was the first to spread the use of GUIs capillary over the world, promoted the use of the mouse to make people understand how easy and immediate it was to use devices that seemed magical to the most. Gates has built the first true software house; he also established the figure of the software engineer who today represents the employment of more than 22 million people around the world\textsuperscript{\cite{22MilSoft}}. \\
Microsoft can be defined as one of the most important pioneers in the field of computer applications, which is still continuing its growth process started in 1975. In fact, Microsoft has not stopped aspiring to innovation and the creation of new technologies because, as Satya Nadella said in 2014, on his first day as new CEO of Microsoft: "The technology industry does not respect tradition – it only respects innovation"\textsuperscript{\cite{NadellaCitation}}. \\
Bill Gates’ life as genius of innovation did not stop to Microsoft: in 2000, he and his wife Melinda founded the Bill \& Melinda Gates Foundation. Thanks to this foundation, the philanthropist shows his continuous striving for innovation in the society itself. It promotes research in technology, medicine, education and development for backward countries. Together with his friend Warren Buffet, he created 'The Given Pledge' which consists of the commitment, together with 175 of the world's wealthiest individuals, to give most of their assets to charity in order to promote the development of the population\textsuperscript{\cite{TheGivenPledge}}. Gates, still today, despite having already achieved his grandiose goals some time ago, is active in the field of advancement and progress and remains an example for all young dreamers.