The traits previously described can be perfectly mirrored on Bill Gates, his behavior and his whole life. During his career Gates showed a great Openness To Experiences, so much that since when he was young he tried several small jobs to feed his curiosity in computer science. This trait will also appear at a later age when, after Microsoft's resounding successes, he decided to come across a completely new field by touching the world's problems at first hand through active participation in charity. Conscientiousness is probably one of the traits that best clarifies the character personality: in addition to being extraordinarily active and focused on the goal, he put a so high attention on the final product that for the first years of Microsoft, despite being CEO, personally controlled every single line of code issued. Extraversion is an aspect of Bill Gates that is plain to see nowadays as it is always at the forefront of promoting young innovators, arguing that this is the best time to aspire to be an innovator.\textsuperscript{\cite{BestMomentInnvators}} According to him, the modern technological moment, which owes a lot to Bill Gates himself, is perfect for developing ideas and pursuing dreams. What probably not everyone knows is that it is only thanks to his extraversion and ability to talk and convince others that Gates is where he is today; most of his fortune came from when he managed to convince IBM, a leading company in the IT market even at the time, not to buy the rights of the MS-DOS operating system, exactly what made the Windows Dynasty begin. However Gates did not excel in Agreeableness and Neuroticism as it was often contradictory and irascible towards many of his colleagues. \\
Despite these remarkable features Gates was extremely competent in his field and had high Cognitive Abilities as can be seen from the fact that before enrolling in college he was rated 1590 out of 1600 at SAT test (Suite of Assessments Test). Gates's extreme knowledge and his constant determination to expand it were the basis of his success with Microsoft. At the time, in fact, he was personally called to work on the product, having to compete with other companies, so a deep ability, knowledge and curiosity were essential to succeed. Throughout his career at Microsoft Gates showed his genius; he was always the first to propose new types of software, giving the possibility to write using Office Word or surf the internet in a fluid way with Internet Explorer. This ability to be one step ahead has made it possible for Microsoft to grow into the leading company it is today. He has really given a decisive push forward to the technological revolution we have in recent years; in 1999 he had already guessed things like Internet of Things, Mobile Devices and Online Payments.\textsuperscript{\cite{Prediction}} \\
However, even behind the founding of the Bill \& Melinda Foundation, we can recognize the role of the Bill Gates innovator who, from the peak of his fame and influence, seeks to bring wellness to the population and improve totally the world and society. The figure of the innovator can be seen not only in the contribution he has made to the development of innovation itself but also in how much he continues, once he has achieved his first important goal, to strive for the best, for progress. In conclusion, probably no other words can be used to perfectly define Bill Gates: an innovator for future innovators.